Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-06 ms.tex

\maketitle
%----------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%  A B S T R A C T %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}

We fit SDSS DR7 data with models that include assembly bias.

Important points:

-supersedes previous analyses even for standard HOD.

-cannot rule out assembly bias using galaxy clustering.

-some samples favor assembly bias.

\end{abstract}

>>>>

\maketitle
%----------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%  A B S T R A C T %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ARZ: Important points:
% -supersedes previous analyses even for standard HOD.
% -cannot rule out assembly bias using galaxy clustering.
% -some samples favor assembly bias.
\begin{abstract}
We constrain the newly-introduced Decorated HOD model using SDSS DR7 measurements of projected galaxy clustering, $\wprp,$ and number density, $n_{\rm d},$ made from r-band luminosity-threshold samples. The Decorated HOD is a model for the galaxy--halo connection that augments the traditional Halo Occupation Distribution (HOD) by allowing for the possibility of {\em assembly bias}: galaxy luminosity may be correlated with dark matter halo properties besides virial mass $\mvir$ alone. We demonstrate that it is not possible to rule out assembly bias using DR7 measurements of $\wprp$ and $n_{\rm d}.$ Moreover, galaxy samples $\magr<-20, -20.5$ favor strong levels of central galaxy assembly bias: high-concentration halos are more likely to host a central galaxy relative to low-concentration halos of the same $\mvir.$ We rule out zero assembly bias with high significance for these samples. Satellite assembly bias only becomes significant for the faintest sample we study, $\magr<-19.$ We find no evidence for assembly bias in the $\magr<-21$ sample. Because the Decorated HOD subsumes the traditional HOD, and additionally because of errors made in the original analysis of these samples, our results differ from and supersede existing HOD constraints from low-redshift clustering measurements. 
\end{abstract}
